Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-03-15 paper/ms.tex
updating rotation period figures

\include{vc}
\usepackage{microtype}

\usepackage{url}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{multirow}
\bibliographystyle{aasjournal}

@@

To demonstrate the applicability of this model, we apply it to infer the
asteroseismic parameters of the giant star KIC~11615890 observed by the
\kepler\ Mission.
The goal of this example is to show that, even for a low signal-to-noise
dataset with a short baseline, it is possible to infer asteroseismic
parameters with formal uncertainties that are consistent with the parameters
inferred with a much larger dataset.
Looking forward to \tess \citep{Campante:2016}, we will infer $\nu_\mathrm{max}$ and $\Delta\nu$
using only one month of \kepler\ data and compare our results to the results
inferred from the full 4 year baseline of the mission.
For KIC~11615890, the published asteroseismic parameters based on the full
dataset are \citep{Pinsonneault:2014}
\begin{eqnarray}
    \nu_\mathrm{max} = 171.94 \pm 3.62 \,\mu\mathrm{Hz} \quad\mathrm{and}\quad
    \Delta\nu = 13.28 \pm 0.29 \,\mu\mathrm{Hz} \quad.
\end{eqnarray}
We randomly select a month-long segment of \kepler\ data, initialize our
\celerite\ model using a grid search in the parameter space, and then use
\emcee\ \citep{Foreman-Mackey:2013} to sample the joint posterior density for
the full set of parameters.
\Figure{astero-corner} shows the marginalized density for $\nu_\mathrm{max}$
and $\Delta\nu$ compared to the results from the literature.
\dfmtodo{Add some more discussion here.}

@@

>>>>

\include{vc}
\include{figures/rotation}

\usepackage{microtype}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{multirow}
\bibliographystyle{aasjournal}

@@

To demonstrate the applicability of this model, we apply it to infer the
asteroseismic parameters of the giant star KIC~11615890 observed by the
\kepler\ Mission.
The goal of this example is to show that, even for a low signal-to-noise
dataset with a short baseline, it is possible to infer asteroseismic
parameters with formal uncertainties that are consistent with the parameters
inferred with a much larger dataset.
Looking forward to \tess\ \citep{Campante:2016}, we will infer
$\nu_\mathrm{max}$ and $\Delta\nu$ using only one month of \kepler\ data and
compare our results to the results inferred from the full 4 year baseline of
the \kepler\ mission.
For KIC~11615890, the published asteroseismic parameters based on the full
dataset are \citep{Pinsonneault:2014}
\begin{eqnarray}
    \nu_\mathrm{max} = 171.94 \pm 3.62 \,\mu\mathrm{Hz} \quad\mathrm{and}\quad
    \Delta\nu = 13.28 \pm 0.29 \,\mu\mathrm{Hz} \quad.
\end{eqnarray}
We randomly select a month-long segment of \kepler\ data, initialize our
\celerite\ model using a grid search in the parameter space, and then use
\emcee\ \citep{Foreman-Mackey:2013} to sample the joint posterior density for
the full set of parameters.
\Figure{astero-corner} shows the marginalized density for $\nu_\mathrm{max}$
and $\Delta\nu$ compared to the results from the literature.
\dfmtodo{Add some more discussion here.}

@@

To demonstrate this model, we

\rotationperiod
